# General Statistics

Before we delve into the specifics of each candidate, let’s take a look at the activity of each candidate on Twitter during their campaigns.

## Twitter Activity

Below, you will see a graph outlining the number of Twitter messages for each candidate since their announcement. Amara Enyia led all the candidates with over 1500 messages, followed by Lori Lightfoot and Garry McCarthy. Please note that the totals below represent retweets as well as messages from each of the campaigns represented. For some candidates, such as Susana Mendoza and Bob Fioretti, low numbers here may represent the recent dates of their announcements. However, John Kozlar announced in May of 2018 and he has the fewest posts.

```{r include = FALSE, message = FALSE}
library(tidyverse)
library(tidytext)
library(lubridate)
library(igraph)
library(ggraph)
library(widyr)
library(qdapRegex)
library(corrplot)
library(RColorBrewer)
library(gridExtra)
library(DescTools)
library(tm)
# Read the data into memory
mayor <- read.csv('tweets_022719.csv',header=T,sep=',',stringsAsFactors=F)
mayor$created_at <- ymd_hms(mayor$created_at)
mayor$date <- date(mayor$created_at)
# Get the actual candidate names
runners <- read.csv('candidate_names.csv',header=T,sep=',',stringsAsFactors=F)
names(runners) <- c('screen_name','candidate_name')
# Join the names to the candidate data frame
mayor <- left_join(mayor,runners)

candidate_filter <- function(data1,screen,announced){
  # first, screen out for the individual candidate
  candidate <- subset(data1,screen_name == screen)
  # next, screen the set for tweets after the announcement date
  candidate_f <- subset(candidate,date > as.Date(announced))
  return(candidate_f)
}

paul_f <- candidate_filter(mayor,'Paulvallas','2018-05-02')
toni_f <- candidate_filter(mayor,'toniforchicago','2018-09-20')
gery_f <- candidate_filter(mayor,'GeryChico','2018-09-20')
garry_f <- candidate_filter(mayor,'Garry4Chicago','2018-05-21')
lori_f <- candidate_filter(mayor,'LightfootForChi','2018-05-10')
bill_f <- candidate_filter(mayor,'DaleyForMayor','2018-09-17')
lashawn_f <- candidate_filter(mayor,'FordForChi19','2018-10-31')
jerry_f <- candidate_filter(mayor,'joyce4mayor','2018-08-29')
will_f <- candidate_filter(mayor,'DrWillieWilson','2018-03-27')
sue_f <- candidate_filter(mayor,'susanamendoza10','2018-11-14')
bob_f <- candidate_filter(mayor,'BobFiorettiChi','2018-11-16')
ama_f <- candidate_filter(mayor,'amaraforchicago','2018-08-28')
neal_f <- candidate_filter(mayor,'nealsales','2018-04-21')
john_f <- candidate_filter(mayor,'JohnKozlar','2018-05-08')

on_campaign <- bind_rows(paul_f,toni_f,gery_f,garry_f,lori_f,bill_f,lashawn_f,jerry_f,will_f,sue_f,bob_f,ama_f,neal_f,john_f)
```
```{r echo=FALSE}
on_campaign %>% group_by(candidate_name) %>% summarise(messages = n_distinct(status_id)) %>% ggplot(aes(reorder(candidate_name,messages),messages))+geom_col(color='black',fill='red')+coord_flip()+theme(axis.text.y = element_text(size=12,face='bold'))+labs(title='Number of Twitter messages since date of announcement',x="")
```


We can also look at the number of posts by each candidate on a monthly basis.

```{r include = FALSE, message = FALSE}
my_month <- on_campaign %>% select(candidate_name,date) %>% group_by(candidate_name,month = floor_date(date,'month')) %>% summarise(month_total = n()) %>% ggplot(aes(x=month,y=month_total,fill=candidate_name))+geom_col(show.legend=FALSE)+scale_x_date(labels=scales::date_format("%b"))+facet_wrap(~candidate_name,scales='free')+ylab('')+xlab('')+ggtitle('Twitter posts per month by candidate since declaring candidacy')
```
```{r echo=FALSE, fig.height=6, fig.width=9}
plot(my_month)
```

As stated earlier, data for each candidate were selected for study from each person’s announcement date until the day the data were downloaded, February 27, 2019. As time went on in each campaign, most candidates increased their number of posts per month. Most candidates built up their number 
of posts gradually as their campaign progressed. Others, like John Kozlar and Neal Sales-Griffin, suddenly increased their activity toward the end of their campaigns.

Finally, we can look at the average number of Twitter posts per campaign day.

```{r include = FALSE, message = FALSE}
sent_out <- read.csv('feb_message_rate.csv',header=T,sep=',',stringsAsFactors=F)
sent_out_plot <- sent_out %>% arrange(messages_per_day) %>% mutate(name = factor(name,levels = .$name)) %>% ggplot(aes(messages_per_day,name,label=paste0(round(messages_per_day,2))))+geom_segment(aes(x=0,y=name,xend=messages_per_day,yend=name),color='lightblue')+geom_point(color='lightblue',size=7)+geom_text(color='black',size=3)+labs(x='Average # of messages per day',y='',title='Average Number of Twitter Messages per Campaign Day \nby Candidate')+theme_minimal()+theme(axis.text.y = element_text(size=12,face='bold'))
```
```{r echo=FALSE}
plot(sent_out_plot)
```

Amaya Enyia’s daily activity places her first in this category, averaging more than three posts than the next candidate. The averages for Bob Fioretti and Susana Mendoza show that, despite their late announcement dates, they had every intention to engage the public via Twitter. In contrast, Neal Sales-Griffin averaged a little over a message per campaign day. Not to be outdone, John Kozlar averages less than half a message per day, even with increased activity in January and February.

