#Hashtag Networks

The use of hashtags also help in forming a narrative and clarifying a stance
taken in a campaign. In this section, we will take a look at how each of the
candidates use hashtags to communicate with potential voters.

## Process and Code

In the dataset from Twitter, hashtags are recorded in a seperate variable, as 
well as being part of the text. The hashtags from each tweet are taken from this
variable, and a similar procedure to the processing of word networks is used to 
build networks of co-occuring hashtags. However, a hashtag would only have to 
appear at least twice to be used.

```{r include = FALSE, message = FALSE}
candidate_hash <- function(candidate_f){
  subj_hash <- candidate_f$hashtags
  subj_hash <- subj_hash[subj_hash != '']
  subj_hash <- as.data.frame(subj_hash)
  subj_hash_bigram <- subj_hash %>% unnest_tokens(bigram,subj_hash,token='ngrams',n=2)
  subj_hash_separated <- subj_hash_bigram %>% separate(bigram,c('word1','word2'),sep=' ')
  subj_hash_counts <- subj_hash_separated %>% count(word1,word2,sort=T)
  subj_hash_map <- subj_hash_counts %>% filter(n > 1) %>% graph_from_data_frame() %>% ggraph(layout='fr')+geom_edge_link(aes(edge_alpha=n,edge_width=n),edge_colour='darkred')+geom_node_point(color='darkslategray4',size=3)+geom_node_text(aes(label=name),vjust=1.8,size=3)+theme_void()
  return(subj_hash_map)
}
paul_hash <- candidate_hash(paul_f)
paul_hash <- paul_hash+labs(title='Hashtag Network: Paul Vallas')

toni_hash <- candidate_hash(toni_f)
toni_hash <- toni_hash+labs(title='Hashtag Network: Toni Preckwinkle')

gery_hash <- candidate_hash(gery_f)
gery_hash <- gery_hash+labs(title='Hashtag Network: Gery Chico')

garry_hash <- candidate_hash(garry_f)
garry_hash <- garry_hash+labs(title='Hashtag Network: Garry McCarthy')

lori_hash <- candidate_hash(lori_f)
lori_hash <- lori_hash+labs(title='Hashtag Network: Lori Lightfoot')

bill_hash <- candidate_hash(bill_f)
bill_hash <- bill_hash+labs(title='Hashtag Network: Bill Daley')

lashawn_hash <- candidate_hash(lashawn_f)
lashawn_hash <- lashawn_hash+labs(title='Hashtag Network: La Shawn K Ford')

jerry_hash <- candidate_hash(jerry_f)
jerry_hash <- jerry_hash+labs(title="Hashtag Network: Jerry Joyce")

will_hash <- candidate_hash(will_f)
will_hash <- will_hash+labs(title="Hashtag Network: Willie Wilson")

sue_hash <- candidate_hash(sue_f)
sue_hash <- sue_hash+labs(title="Hashtag Network: Susana Mendoza")

ama_hash <- candidate_hash(ama_f)
ama_hash <- ama_hash+labs(title="Hashtag Network: Amara Enyia")

neal_hash <- candidate_hash(neal_f)
neal_hash <- neal_hash+labs(title="Hashtag Network: Neal Sales-Griffin")

john_hash <- candidate_hash(john_f)
john_hash <- john_hash+labs(title="Hashtag Network: John Kozlar")

bob_hash <- candidate_hash(bob_f)
bob_hash <- bob_hash+labs(title="Hashtag Network: Bob Fioretti")

```

### Bob Fioretti

Besides the requesite hashtags tying Bob Fioretti with the Mayoral
election, there are at least a couple of hastags connecting Toni
Preckwinkle with Ed Burke.

```{r echo=FALSE}
plot(bob_hash)
```

### John Kozlar

John Kozlar's Twitter feed does not have many hashtags, but the hashtag
network still ties him to being against corruption and the candidacy of a certain participant.

```{r echo=FALSE}
plot(john_hash)
```

### Neal Sales-Griffin

The hashtag network of Neal Sales-Griffin has few hashtags. Apparently, 
though, a significant number of them refer to his podcast.

```{r echo=FALSE}
plot(neal_hash)
```

### Amara Enyia

Amara Enyia's hashtag network is notable for frequent references to
people (allpeople, peoplepower, etc.).

```{r echo=FALSE}
plot(ama_hash)
```

### Susana Mendoza

The hashtag network of Susana Mendoza is unique among all. She 
has seemingly tied the majority of her hashtags to the hashtag chimayor19.

```{r echo=FALSE}
plot(sue_hash)
```


### Willie Wilson

To a large extent, Willie Wilson's hashtags center on the election and 
his desire to be elected. However, there are also more than a few of
religious themed hashtags, as well as references to the Jason Van Dyke
trial involving the killing of Laquan McDonald.

```{r echo=FALSE}
plot(will_hash)
```

### Jerry Joyce

Jerry Joyce also seems to have a number of hashtags connected to a central
theme: electing Jerry Joyce as mayor. There are also a few instances of 
hastags referring to the Chicago Bears of the NFL.

```{r echo=FALSE}
plot(jerry_hash)
```

### La Shawn K Ford

Most of the hashtags in this network center on the election and the candidate.
The presence of several transit related hastags is unique among the other
networks.

```{r echo=FALSE}
plot(lashawn_hash)
```

### Bill Daley

Beyond hashtags, there really isn't much to work with in Bill Daley's Hashtag Network.

```{r echo=FALSE}
plot(bill_hash)
```




### Lori Lightfoot

The network of Lori Lightfoot support her asertations as being progressive, 
with references to a universal basic income, housing concerns, the LGBTQ 
community, and her possible stance on the TIF's.

```{r echo=FALSE}
plot(lori_hash)
```

### Garry McCarthy

Garry McCarthy's network is unique due to a number of references to the 
present Mayor, Rahm Emanuel.

```{r echo=FALSE}
plot(garry_hash)
```

### Gery Chico

The network of Gery Chico is comparable to the others in the campaign. However,
there are several hashtags referring to the rights of the disabled.

```{r echo=FALSE}
plot(gery_hash)
```

### Toni Preckwinkle

In addition to the LGBTQ community and housing, the hastag network of Toni Preckwinkle 
is interesting in its references to the "blue wave" elections of 2018.

```{r echo=FALSE}
plot(toni_hash)
```

### Paul Vallas

Besides encouraging people to vote, Paul Vallas' network is notable for its focus
on commerce, budgeting, and public safety.  

```{r echo=FALSE}
plot(paul_hash)
```

