# Candidate Correlation

In this section, we will examine how similar are the terms that the candidates use. With the pairwise_cor() function from the widyr package, we can compare the words that the candidates
use, as well as their frequency of use. To do this, we will use the code below to create a correlation matrix, comparing each candidate. We’ll also add coefficients of 1 to compare candidates to themselves.

```{r messages=FALSE, warning = FALSE}
cleaned_text <- on_campaign %>% filter(!is_retweet) %>%
mutate(text = str_remove_all(text,remove_reg)) %>% mutate(text = rm_twitter_url(text)) %>% mutate(text = rm_hash(text)) %>% unnest_tokens(word,text) %>% filter(!word %in% stop_words$word) %>% filter(!word %in% my_stopwords$word)
cleaned_text2 <- cleaned_text[!grepl("toni|preckwinkle|paul|vallas|gery|chico|garry|mccarthy|lori|lightfoot|bill|daley|amara|enyia|bob|fioretti|jerry|joyce|la|shawn|ford|neal|sales-griffin|dr|willie|wilson|john|kozlar",cleaned_text$word),]
words_to_candidate <- cleaned_text2 %>% count(candidate_name,word,sort=T) %>% ungroup()
message_cors <- words_to_candidate %>% pairwise_cor(candidate_name,word,n,sort=T)
name1 <- unique(as.character(mayor$candidate_name))
name2 <- unique(as.character(mayor$candidate_name))
self_score <- as.numeric(rep(1,14))
self_score_result <- data.frame(cbind(name1,name2,self_score),stringsAsFactors=F)
names(self_score_result) <- c('item1','item2','correlation')
self_score_result$correlation <- as.numeric(self_score_result$correlation)
message_cors2 <- bind_rows(message_cors,self_score_result)
candidate_matrix <- xtabs(correlation~.,message_cors2)
candidate_matrix2 <- as.matrix.xtabs(candidate_matrix)
```

Below are a few rows of the correlations among the candidates, with regard to the terms used and 
their frequency of use

```{r include = FALSE}
dfcorr <- message_cors2[1:6,]
```
```{r echo=FALSE, warning = FALSE}
kable(dfcorr) %>% kable_styling(bootstrap_options = 'striped',full_width=F)
```


Once the matrix is built, we can use the corrplot() function to visually represent the correlations.

```{r echo=FALSE, warning = FALSE}
corrplot(candidate_matrix2,order='hclust',cl.lim=c(0,1),col = rep(rev(brewer.pal(n=8,name='PuOr')),2),tl.col='black')
```

Our results show that there is a definite core group of candidates who highly correlate with each other. You've probably also noted that none of the candidates negatively correlate with each other.
Since all of them are campaigning for the same position, within the same city, responding to 
similar issues, you would expect a certain similarity among the candidates. Still, there are notable
differences among them.
