# Sentiment Analysis

One way to evaluate the messaging done by candidates is to gauge
the emotion and opinion behind their statements. In this section 
we will be examining aspects of the sentiment of each candidate's 
messages throughout their campaigns.

## How we will measure sentiment

We will use the AFINN Lexicon, from Finn Arup Nielsen to examine the
terms used in the candidate's tweets. Detailed information on the lexicon
can be found in the paper _A_ _new_ _ANEW:_ _evaluation_ _of_ _a_ _word_ _list_ _for_ 
_sentiment analysis in microblogs?, proceedings of the ESWC 2011 Workshop_.
A copy of the paper can be found [here](http://corpustext.com/reference/sentiment_afinn.html).
Simply put, the lexicon rates terms used as being either "positve" or "negative". 
The score for each term is within a range of -5 (very negative) to 5 (very positive).

## Average term score by candidate

For example, we can look at the average score for each term used by the 
candidates in their twitter messages during each of their campaigns.
The code below with take each term used by the candidates, assign a 
score from the AFINN Lexicon for each term it shares in the candidate's 
tweet, multiply the scores by the number of times each term is used
(we'll call this contribution to sentiment), and divides that result by the total number 
of terms appearing in the messages.

```{r messages = FALSE, echo = FALSE}
message_sentiments <- words_to_candidate %>% inner_join(get_sentiments('afinn'),by='word') %>% group_by(candidate_name) %>% summarise(score = sum(score*n)/sum(n))

```
```{r include = FALSE}
avg_sent <- message_sentiments %>% mutate(candidate_name = reorder(candidate_name,score)) %>% ggplot(aes(candidate_name,score))+
geom_col(show.legend=F,color='black',fill='red')+coord_flip()+ylab('Average Score')+xlab('')+theme(axis.text = element_text(color='black'),axis.text.y = element_text(size=12,face='bold'))+ggtitle("Average Sentiment Score per Term")
```
```{r echo=FALSE}
plot(avg_sent)
```

The results show that Willie Wilson is the most "positive", 
averaging a score of over one per term used. Candidate Wilson is followed 
by John Kozlar and Neal Sales-Griffin. The least "positive" on average, by far, is Garry McCarthy.

## Highest Contributions to Sentiment

At this point, you might be asking what are the words that are making these 
messages positive or negative. The following code will extract the 25 words 
from all of the timelines that, by their frequency of use and assigned score, are most 
prominent in contributions made to overall twitter message sentiment. This will 
include both prominent positive and negative words.

```{r eval = FALSE}
message_contributions <- cleaned_text2 %>% inner_join(get_sentiments('afinn'),by='word') %>% group_by(word) %>%
summarise(occurences = n(),contribution = sum(score))
message_contributions %>% top_n(25,abs(contribution)) %>% mutate(word=reorder(word,contribution)) %>%
ggplot(aes(word,contribution,fill=contribution > 0))+geom_col(show.legend=F)+theme(axis.text = element_text(color='black'))+coord_flip()+ggtitle('Top 25 words contributing to message sentiment')
```
```{r include = FALSE}
message_contributions <- cleaned_text2 %>% inner_join(get_sentiments('afinn'),by='word') %>% group_by(word) %>%
summarise(occurences = n(),contribution = sum(score))
message_contributions <- message_contributions %>% top_n(25,abs(contribution)) %>% mutate(word=reorder(word,contribution))
top_sent <- ggplot(message_contributions,aes(word,contribution,fill=contribution > 0))+geom_col(show.legend=F)+theme(axis.text = element_text(color='black'))+coord_flip()+ggtitle('Top 25 words contributing to message sentiment')
```
```{r echo=FALSE}
plot(top_sent)
```

As you can see, the words "suport" and "happy" are the most prominient of the positive
words contributing to sentiment. Meanwhile, "crime" and "violence" and the most prominent negative words.

## Top Contributions to Sentiment by Candidate

We can do something similar for each of the candidates. Below are the plots for each 
candidate indicating the top twelve words for their timelines by their contribution to
sentiment (again, score times number of times used). If there are ties in contribution, 
all tied words are used.

```{r include = FALSE}
top_impact_words <- words_to_candidate %>% inner_join(get_sentiments('afinn'),by='word') %>% group_by(candidate_name) %>% mutate(totals = n*score) %>% top_n(12,abs(totals)) %>% group_by(candidate_name,word)
candidate_impact_words <- function(aspirant){
  word_plot <- top_impact_words %>% ungroup() %>% filter(candidate_name == aspirant) %>% top_n(12,abs(totals)) %>% mutate(word = reorder(word,totals)) %>% ggplot(aes(word,totals,fill = totals > 0))+geom_col(show.legend=F)+labs(x='',y='',title=aspirant)+theme(axis.text.y = element_text(size=10), plot.title = element_text(hjust=.5),panel.background = element_rect(fill = 'lightgray'))+coord_flip()
  return(word_plot)
}
ama_i <- candidate_impact_words('Amara Enyia')
bill_i <- candidate_impact_words('Bill Daley')
bob_i <- candidate_impact_words('Bob Fioretti')
garry_i <- candidate_impact_words('Garry McCarthy')
gery_i <- candidate_impact_words('Gery Chico')
jerry_i <- candidate_impact_words("Jerry Joyce")
lashawn_i <- candidate_impact_words("La Shawn K Ford")
lori_i <- candidate_impact_words("Lori Lightfoot")
neal_i <- candidate_impact_words("Neal Sales-Griffin")
paul_i <- candidate_impact_words("Paul Vallas")
sue_i <- candidate_impact_words("Susana Mendoza")
toni_i <- candidate_impact_words("Toni Preckwinkle")
will_i <- candidate_impact_words("Willie Wilson")
john_i <- candidate_impact_words("John Kozlar")
```
```{r echo=FALSE,fig.height=7.5,fig.width=9.5}
grid.arrange(ama_i,bill_i,bob_i,garry_i,gery_i,jerry_i,lashawn_i,lori_i,neal_i,paul_i,sue_i,toni_i,will_i,john_i,ncol=4)
```

The results give some insight as to why Willie Wilson and 
Garry McCarthy are at the extremes in terms of average score per term.

## Highest (and Lowest) Average Scoring Tweets

Besides looking at individual words, we can assess the average sentiment score for a given 
tweet. In the code below, we can ascertain the average score per term tweet for each tweet 
in the dataset. We'll try to take the top scoring tweets, as well as the lowest scoring tweets.
**In a later version of this document, I plan to include average scores with the tweets**.

```{r message = FALSE, echo = FALSE, include = FALSE}
my_campaign <- on_campaign %>% filter(!is_retweet) %>% select(candidate_name,status_id,text) %>% mutate(text = str_remove_all(text,remove_reg)) %>% mutate(text = rm_twitter_url(text)) %>% mutate(text = rm_hash(text))
my_campaign2 <- my_campaign %>% unnest_tokens(word,text) %>% filter(!word %in% stop_words$word) %>% filter(!word %in% my_stopwords$word)
sentiment_messages <- my_campaign2 %>% inner_join(get_sentiments('afinn'), by = 'word') %>% group_by(candidate_name,status_id) %>% summarise(sentiment = mean(score), words = n()) %>% ungroup() %>% filter(words >= 3)
message_pos <- sentiment_messages %>% arrange(desc(sentiment)) %>% top_n(10,sentiment)
message_neg <- sentiment_messages %>% arrange(desc(sentiment)) %>% top_n(-10,sentiment)
message_pos_table <- on_campaign %>% select(candidate_name,status_id,text) %>% filter(on_campaign$status_id %in% message_pos$status_id) %>% left_join(select(message_pos,sentiment,status_id),by="status_id")
message_neg_table <- on_campaign %>% select(candidate_name,status_id,text) %>% filter(on_campaign$status_id %in% message_neg$status_id) %>% left_join(select(message_neg,sentiment,status_id),by="status_id")
```

Below are the tweets with the top average sentiment scores.

```{r echo = FALSE}
message_pos_table %>% select(candidate_name,status_id,text,sentiment) %>% kable() %>% kable_styling(bootstrap_options = 'striped', full_width=F) %>% column_spec(1,bold=T) %>% 
  column_spec(2,border_right=T) %>% column_spec(3,width="30em")
```

And here are the tweets with the lowest average sentiment scores.

```{r echo = FALSE}
message_neg_table %>% select(candidate_name,status_id,text,sentiment) %>% kable() %>% kable_styling(bootstrap_options = 'striped', full_width=F) %>% column_spec(1,bold=T) %>% 
  column_spec(2,border_right=T) %>% column_spec(3,width="30em")
```
