--- 
title: "Data Visualization and Analysis of Twitter use among the 2019 Chicago Mayoral Election Candidates"
author: "Pierre Phanor"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: 
biblio-style: apalike
link-citations: yes
github-repo:
description: "Visualizing how the 2019 Chicago Mayoral Candidates used Twitter during their campaigns."
---

# Preface

The 2019 Chicago Mayoral Election is scheduled to take place on 
February 26. On that day, residents will be making decisions
on the people who will lead the city and chart its course in the face of issues 
such as Crime, Pension Obligations, and Affordable Housing. The goal
of this project is to analyze how the candidates communicate to Chicago's
residents through Twitter and, hopefully, gleam some insight into
each candidate's vision for the city.

## Acknowledgements

Simply put, I would not have been motivated to do this project
without the book *Text Mining with R*, written by Julia Silge and 
David Robinson, and their tidytext package. Most of the techniques 
used in this document are from the book. Text Mining with R serves
as a insightful and concise entry into Natural Language Processing.

Along with the tidytext package, I should take this time to recognize
the other packages used in the document.

* tidyverse
* lubridate
* igraph
* ggraph
* widyr
* qdapRegex
* corrplot
* RColorBrewer
* gridExtra
* DescTools
* tm

## Candidates Covered

Below is a table of the candidates for Chicago City Mayor as of January 
31, 2019. Included with their names are their present or previous positions.

```{r include=FALSE}
dtcand <- data.frame(Candidate=c('Bob Fioretti','La Shawn K Ford','Susana Mendoza','Toni Preckwinkle','Gery Chico','Bill Daley','Lori Lightfoot','Garry McCarthy','Paul Vallas','Amara Enyia','Jerry Joyce','John Kozlar','Neal Sales-Griffin','Willie Wilson'),Background=c('Former Alderman','State Representative','Illinois Comptroller','Cook County Board President','Former Chicago Public Schools President','Former U.S. Commerce Secretary','Former Chicago Police Board President','Former Chicago Police Superintendent','Former Chicago Public Schools CED','Director of Austin Chamber of Commerce','Lawyer','Lawyer','Tech Entrepreneur','Buisnessman'),Username=c('BobFiorettiChi','FordForChi19','susanamendoza10','toniforchicago','GeryChico','DaleyForMayor','LightfootForChi','Garry4Chicago','Paulvallas','amaraforchicago','joyce4mayor','JohnKozlar','nealsales','DrWillieWilson'),Campaign_Start=c('11/26/18','10/31/18','11/14/18','9/20/18','9/20/18','9/17/18','5/10/18','5/21/18','5/2/18','8/28/18','8/29/18','5/8/18','4/21/18','3/27/18'))
```
```{r include = FALSE}
kable(dtcand) %>% kable_styling(full_width=T) %>% column_spec(1,bold=T,border_right=T)
```

## Code Examples

In the document, I will try to highlight some of the underlying code
for the analysis to illustrate how the data were processed. The full 
code for the analysis will be made available on Github, as well 
as the datasets used.

## Outline

In Chapter 2, we will go over some of the basic statistics involved with
the candidate's Twitter use. 

Chapter 3 will introduce the word networks associated with each of the
candidates. The goal of each network is to illustrate relationships of
terms and how those relationships highlight narratives in the campaign.

We'll do the same in Chapter 4, but this time with hashtags. Hashtags can
also help convey a candidate's stance, but in a more concise and connected
way.

In Chapter 5, we will look at examples of Word Associations. Word Associations will help
to correlate issues facing Chicago and related terms used during the campaign season.

For Chapter 6, We will take a quick look to see how similar the candidates are
with respect to the terms they use and their frequency of use.

Finally, in Chapter 7 we will look perceived positive and negative sentiment
in the messages the candidates use.

## Data Acquisition

The Data were acquired from Twitter through use of the Twitter Developer
App and the rtweet package from R. By using the rtweet package, we were
able to access the Twitter API and download, potentially, up to the last 
3200 tweets from each candidate's Twitter feed with the get_timeline() function. 
The collected data were, then, converted to a comma delimited file for 
portability and easier access. Data for each candidate in the analysis covers the
time from their announcement date until the day the data were downloaded, January 31, 2019.
More information on Twitter Developer Apps can be found [here](https://deveolper.twitter.com).

